A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-04-27 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

		    @ Anoher case is that, processes are information closed but it is trivial.

>>>>

		    @ Another case is that, processes are information closed but it is trivial.

		    @ Even though the system can form NTIC processes in some certain coarse-grained levels, information processing outside these levels remains unconscious.

		    @ microscopic neural activities fall in this category.

		    @ When processes at macroscopic levels becomes informational closed, information from other levels is redundant.

		    @ Therefore, information from other levels does not influence the dynamic of this level.
